---
title: "MB_Map_Bathimetry"
author: "Katie Pitz"
date: "3/6/2020"
output: html_document
---

```{r}
#library(marmap) #if want to download data from NOAA quickly - lower res
library(ggplot2)
library(mapdata)
library(mapproj)
library(ggsn) #just for scale bar
#library(ggspatial)
library(dplyr)


library(qiime2R)
library(tidyverse)
#library(readr) #read csv files
library(lubridate) #for date modifications
#library(vegan)
#library(dplyr)
#library(ggplot2)
library(ggthemes)
library(magrittr)
#library(tidyr)
#for heatmap section
library(gridExtra)
library(RColorBrewer) #colors for plotting
library(forcats) #working with factor data (reordering)
library(patchwork) #putting graphs together on same plot
```

# Set Constants
```{r}
marker = sym("12S")
# Set directory to save plots
plot_directory <- '../figures/Map/'
# Set directory to retrieve data
data_directory = "../Data/filtered_seq_data/"
```

# Import Data

```{r}
#metadata table
print('metadata table')
#file = "A2W_12S_meta_Filtered.csv"
file = paste("CN19S_",marker,"_meta_filtered.csv", sep='')
filepath = paste(data_directory, file, sep='')
print(filepath)
samp.c <- read_csv(filepath) %>% rename('SampleID' = 1)

```
# Edit metadata
```{r}
meta <- samp.c %>% 
  # create date/time format column from local time
  mutate(time = ymd_hms(local_time)) %>%
  mutate(time_since = as.numeric(time)) %>%
  mutate(ESP = case_when(str_detect(SampleID, 'SC')==TRUE ~'ESP',
                         str_detect(SampleID, 'Bongo')==TRUE ~'Bongo',
                         str_detect(SampleID, '_V')==TRUE ~'ROV',
                         TRUE~'CTD')) %>%
  mutate(month =  month(time)) %>%
  mutate(hour = hour(time)) %>%
  mutate(day =  day(time)) %>%
  mutate(year =  year(time)) %>%
  mutate(jday = yday(time)) %>%
  mutate(month_char = as.character(month)) %>%
  mutate(year_char = as.character(year)) %>%
  mutate(depth_bin = case_when(depth <=25 ~ "00_0-25m",
                               depth >25 & depth <=75 ~ "01_25-75m",
                               #depth >50 & depth <=75 ~ "02_50-75m",
                               depth >75 & depth <=100 ~ "03_75-100m",
                               depth >100 & depth <=150 ~ "04_100-150m",
                               depth >150 & depth <=200 ~ "05_150-200m",
                               depth >200 & depth <=250 ~ "06_200-250m",
                               depth >250 & depth <=300 ~ "07_250-300m",
                               depth >300 & depth <=400 ~ "08_300-400m",
                               depth >400 & depth <=500 ~ "09_400-500m",
                               depth >400 & depth <=600 ~ "10_500-600m",
                               depth >600 & depth <=750 ~ "11_600-750m", TRUE ~ "unknown"
  )) 
```



# Define reference points
```{r}
# make a few points
pts = data.frame(
  lon = c(-121.8466667, -122.02, -122.187028),
  lat = c(36.79666667, 36.735, 36.71211),
  label = c('C1', 'M1',  'MARS')
)

mars = data.frame(
  lon = c(-122.187028),
  lat = c(36.71211),
  label = c('MARS')
)

```

# Define bathymetry
```{r}
# # get bathymetry data
# b = getNOAA.bathy(lon1 = -120, lon2 = -124, lat1 = 35, lat2 = 38, 
#                   resolution = 1)
# 
# # convert bathymetry to data frame
# bf = fortify.bathy(b)

###  OR import better bathymetry data
#go to this link:
#https://sccoos.org/data/bathy/?region=monterey
#download lat/lon/depth zipped data file
#file location
file = '/Users/kpitz/Projects/Maps/monterey.xyz'
# csv has lat, lon, depth columns
library(readr)
bf = read_csv(file, col_names=c("x", "y", "z"))
#Divins, D.L., and D. Metzger, NGDC Coastal Relief Model, Retrieved date goes here, http://www.ngdc.noaa.gov/mgg/coastal/coastal.html. Download provided by the Southern California Coastal Ocean Observing System http://sccoos.org/data/bathy


# get regional polygons
reg = map_data("world2Hires")
#reg = subset(reg, region %in% c('USA'))

# convert lat longs
reg$long = (360 - reg$long)*-1


# set map limits
lons = c(-122.7, -121.85)
lats = c(36.55, 37.1)


# #create for scale bar
# df <- filter(reg,long < -121.85 )
# df <- filter(df,long > -122.7 )
# df <- filter(df,lat < 37.1 )
# df <- filter(df,lat > 36.55 )
```
# Plot Filled Contour Map - by sampling type, zoom MARS
```{r}
# DEPTH CONTOURS
# set map limits
#lons = c(-122.5, -121.80)
#lats = c(36.55, 37.0)

# zoomed in
lons = c(-122.3, -122.1)
lats = c(36.6, 36.8)

#lons = c(-122.25, -122.10)
#lats = c(36.7, 36.74)

plot1 <- ggplot()+
  # geom_contour_filled(data = bf,
  #              aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-500,-750,-1000,-1500, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m", "0-500m",
                               "500-750m",
                               "750-1000m",
                               "1000-1500m",
                               "1500-2000m",
                               "2000-3500m")) +
  geom_point(data = meta %>% filter(ESP %in% c('ESP')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "yellow",fill='yellow',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(ESP %in% c('CTD')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "orange",fill='orange',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('WESTERN FLYER')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "green",fill='green',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('ROV')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "purple",fill='purple',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
  geom_text(data = mars, aes(x = lon, y = lat, label=label),
            size=3, vjust=2.5, fontface = "bold", color='black') +
  geom_point(data = mars, aes(x = lon, y = lat),
            colour = "black",fill='black',
            stroke = .5, size = 1.5,
            alpha = 1, shape = 21)+
  # geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
  #           colour = "black",fill='grey',
  #           stroke = 0.5, size = 2,
  #           alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

plot1
filename <- paste(plot_directory, 'DVM_contour_map_ESP_zoomMARS.png', sep='')
ggsave(filename)
filename <- paste(plot_directory, 'DVM_contour_map_ESP_zoomMARS.svg', sep='')
ggsave(filename)

```
# Plot Filled Contour Map - by sampling type
```{r}
# DEPTH CONTOURS
# set map limits
lons = c(-122.5, -121.80)
lats = c(36.55, 37.0)

# zoomed in
# lons = c(-122.3, -121.8)
# lats = c(36.6, 36.8)

# lons = c(-122.25, -122.10)
# lats = c(36.7, 36.74)

plot1 <- ggplot()+
  # geom_contour_filled(data = bf,
  #              aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-500,-750,-1000,-1500, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m", "0-500m",
                               "500-750m",
                               "750-1000m",
                               "1000-1500m",
                               "1500-2000m",
                               "2000-3500m")) +
  geom_point(data = meta %>% filter(ESP %in% c('ESP')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "yellow",fill='yellow',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(ESP %in% c('CTD')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "orange",fill='orange',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('WESTERN FLYER')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "green",fill='green',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('ROV')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "purple",fill='purple',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
  geom_text(data = mars, aes(x = lon, y = lat, label=label),
            size=3, vjust=2.5, fontface = "bold", color='black') +
  geom_point(data = mars, aes(x = lon, y = lat),
            colour = "black",fill='black',
            stroke = .5, size = 1.5,
            alpha = 1, shape = 21)+
  # geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
  #           colour = "black",fill='grey',
  #           stroke = 0.5, size = 2,
  #           alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

plot1
filename <- paste(plot_directory, 'DVM_contour_map_ESP_MB.png', sep='')
ggsave(filename)
filename <- paste(plot_directory, 'DVM_contour_map_ESP_MB.svg', sep='')
ggsave(filename)

```

# Plot Filled Contour Map - by sampling type
```{r}
# DEPTH CONTOURS
# set map limits
#lons = c(-122.5, -121.80)
#lats = c(36.55, 37.0)

# zoomed in
lons = c(-122.3, -121.8)
lats = c(36.6, 36.8)

#lons = c(-122.25, -122.10)
#lats = c(36.7, 36.74)

plot1 <- ggplot()+
  # geom_contour_filled(data = bf,
  #              aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-500,-750,-1000,-1500, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m", "0-500m",
                               "500-750m",
                               "750-1000m",
                               "1000-1500m",
                               "1500-2000m",
                               "2000-3500m")) +
  geom_point(data = meta %>% filter(ESP %in% c('ESP')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "yellow",fill='yellow',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(ESP %in% c('CTD')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "orange",fill='orange',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('WESTERN FLYER')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "green",fill='green',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('ROV')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "purple",fill='purple',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
  geom_text(data = pts, aes(x = lon, y = lat, label=label),
            size=3, vjust=2.5, fontface = "bold", color='black') +
  geom_point(data = pts, aes(x = lon, y = lat),
            colour = "black",fill='black',
            stroke = .5, size = 1.5,
            alpha = 1, shape = 21)+
  # geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
  #           colour = "black",fill='grey',
  #           stroke = 0.5, size = 2,
  #           alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

plot1
filename <- paste(plot_directory, 'DVM_contour_map_ESP_zoom.png', sep='')
ggsave(filename)
filename <- paste(plot_directory, 'DVM_contour_map_ESP_zoom.svg', sep='')
ggsave(filename)

```

# Plot Filled Contour Map - by plate
```{r}
# DEPTH CONTOURS
# set map limits
lons = c(-122.5, -121.80)
lats = c(36.55, 37.0)

#lons = c(-122.25, -122.10)
#lats = c(36.7, 36.74)

test <- meta %>%
  filter(PlateID %in% c('CE', 'BT'))
plot1 <- ggplot()+
  # geom_contour_filled(data = bf,
  #              aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-500,-750,-1000,-1500, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m", "0-500m",
                               "500-750m",
                               "750-1000m",
                               "1000-1500m",
                               "1500-2000m",
                               "2000-3500m")) +
  geom_point(data = meta %>% filter(PlateID %in% c('CE', 'BT')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "yellow",fill='yellow',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(PlateID %in% c('JJ', 'RR')), aes(x = decimalLongitude, y = decimalLatitude, fill=PlateID),
            colour = "orange",fill='orange',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('WESTERN FLYER')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "green",fill='green',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
    # geom_point(data = meta %>% filter(SAMPLING_platform %in% c('ROV')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
    #         colour = "purple",fill='purple',
    #         stroke = .2, size = 1,
    #         alpha = 0.5, shape = 21)+
  geom_text(data = pts, aes(x = lon, y = lat, label=label),
            size=3, vjust=2.5, fontface = "bold", color='black') +
  geom_point(data = pts, aes(x = lon, y = lat),
            colour = "black",fill='black',
            stroke = .5, size = 1.5,
            alpha = 1, shape = 21)+
  # geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
  #           colour = "black",fill='grey',
  #           stroke = 0.5, size = 2,
  #           alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

plot1
filename <- paste(plot_directory, 'DVM_contour_map_plate.png', sep='')
ggsave(filename)
filename <- paste(plot_directory, 'DVM_contour_map_plate.svg', sep='')
ggsave(filename)

```


# Plot contour plot

```{r}
# make plot
# set map limits

lons = c(-122.225, -122.15)
lats = c(36.67, 36.75)

# #create for scale bar
# df <- filter(reg,long < -122.15 )
# df <- filter(df,long > -122.225 )
# df <- filter(df,lat < 36.8 )
# df <- filter(df,lat > 36.6 )

p <- ggplot()+
  
    # add 800m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-800),
               size=c(0.5),
               colour="grey")+
  
  
  # add 1000m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-1000),
               size=c(0.5),
               colour="grey")+
  
  # add points
  geom_point(data = pts, aes(x = lon, y = lat),
            colour = "black", fill= "black",
            stroke = .2, size = 3,
            alpha = 1, shape = 21)+
  
  
  geom_point(data = meta, aes(x = decimalLongitude, y = decimalLatitude,
                              fill=SAMPLING_platform),
            colour = "black",
            stroke = .2, size = 2,
            shape = 21, 
            alpha = 0.8)+
  
  geom_text(data = pts, aes(x = lon, y = lat, label=label),
            size=4, vjust=3.5, fontface = "bold") +
  
  
  # #add labels
  # geom_text(data = pts, aes(x = lon, y = lat),
  #           label=c('C1', 'M1','M2'), size=3, vjust=2.5, fontface = "bold")+
  
  # # add coastline
  # geom_polygon(data = reg, aes(x = long, y = lat, group = group),
  #              fill = "darkgrey", color = NA)  +

  # configure projection and plot domain
  coord_map(xlim = lons, ylim = lats)+
  
  #scale bar
  #scalebar(meta %>% select(decimalLongitude, decimalLatitude), dist = 2, dist_unit = "km",
  #           transform = FALSE, model = "WGS84") +
  
  scalebar(data = meta %>% select(decimalLongitude, decimalLatitude), dist = 2, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  ylab("")+xlab("")+
  theme_bw()
  
filename <- paste(plot_directory, 'DVM_sample_map.png', sep='')
ggsave(filename)
p
filename

```

# SCRAP BELOW

```{r}
# make plot
# set map limits

lons = c(-122.225, -122.15)
lats = c(36.67, 36.75)

p <- ggplot()+
  
  # # add 50m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-50),
  #              size=c(0.3),
  #              colour="grey")+
  # 
  # 
  # # add 100m contour
  # geom_contour(data = bf,
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-100),
  #              size=c(0.3),
  #              colour="grey")+
  # # 
  # # add 150m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-150),
  #              size=c(0.3),
  #              colour="grey")+
  
  # # add 200m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-200),
  #              size=c(0.3),
  #              colour="grey")+
  # # add 300m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-300),
  #              size=c(0.3),
  #              colour="grey")+
  # # add 400m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-400),
  #              size=c(0.3),
  #              colour="grey")+
  # 
  # # add 500m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-500),
  #              size=c(0.5),
  #              colour="grey")+
  
  # add 1000m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-1000),
               size=c(0.5),
               colour="grey")+
  # 
  # # add 2000m contour
  # geom_contour(data = bf, 
  #              aes(x=x, y=y, z=z),
  #              breaks=c(-2000),
  #              size=c(0.5),
  #              colour="grey")+
  # 
  # # add 0m contour
  # geom_contour(data = bf,
  #              aes(x=x, y=y, z=z),
  #              breaks=c(0.5),
  #              size=c(0.5),
  #              colour="black")+
  # add points
  geom_point(data = pts, aes(x = lon, y = lat),
            colour = "black", fill= "black",
            stroke = .2, size = 3,
            alpha = 1, shape = 21)+
  
  
  geom_point(data = meta, aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
            colour = "black",
            stroke = .2, size = 2,
            alpha = 0.8, shape = 21)+
  
  geom_text(data = pts, aes(x = lon, y = lat, label=label),
            size=4, vjust=2.5, fontface = "bold") +
  
  
  # #add labels
  # geom_text(data = pts, aes(x = lon, y = lat),
  #           label=c('C1', 'M1','M2'), size=3, vjust=2.5, fontface = "bold")+
  
  # # add coastline
  # geom_polygon(data = reg, aes(x = long, y = lat, group = group),
  #              fill = "darkgrey", color = NA)  +

  # configure projection and plot domain
  coord_map(xlim = lons, ylim = lats)+
  
  #scale bar
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  ylab("")+xlab("")+
  theme_bw()
  
filename <- paste(plot_directory, 'DVM_sample_map.png', sep='')
ggsave(filename)
p
filename

```
#with contours

```{r}
# DEPTH CONTOURS
# set map limits
lons = c(-122.5, -121.80)
lats = c(36.55, 37.0)

#lons = c(-122.25, -122.10)
#lats = c(36.7, 36.74)

test <- ggplot()+
  # geom_contour_filled(data = bf,
  #              aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-500,-750,-1000,-1500, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m", "0-500m",
                               "500-750m",
                               "750-1000m",
                               "1000-1500m",
                               "1500-2000m",
                               "2000-3500m")) +
  geom_point(data = meta %>% filter(SAMPLING_platform %in% c('daphne')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
            colour = "yellow",fill='yellow',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(SAMPLING_platform %in% c('makai')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
            colour = "orange",fill='orange',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(SAMPLING_platform %in% c('WESTERN FLYER')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
            colour = "green",fill='green',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
    geom_point(data = meta %>% filter(SAMPLING_platform %in% c('ROV')), aes(x = decimalLongitude, y = decimalLatitude, fill=SAMPLING_platform),
            colour = "purple",fill='purple',
            stroke = .2, size = 1,
            alpha = 0.5, shape = 21)+
  geom_text(data = pts, aes(x = lon, y = lat, label=label),
            size=3, vjust=2.5, fontface = "bold", color='black') +
  geom_point(data = pts, aes(x = lon, y = lat),
            colour = "black",fill='black',
            stroke = .5, size = 1.5,
            alpha = 1, shape = 21)+
  # geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
  #           colour = "black",fill='grey',
  #           stroke = 0.5, size = 2,
  #           alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

test
filename <- paste(directory, 'CN19S_contour_map_daphne.png', sep='')
ggsave(filename)
filename <- paste(directory, 'CN19S_contour_map_daphne.svg', sep='')
ggsave(filename)

```

## FINAL PLOTS with CONTOURS
```{r}
# DEPTH CONTOURS
test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m",
                               "300-400m","400-500m","500-1000m",
                               "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth.svg')
#GREYSCALE CONTOURS
test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  scale_fill_brewer(palette = "Greys",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m",
                               "300-400m","400-500m","500-1000m",
                               "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth_grey.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth_grey.svg')

```






```{r}
# make plot
p <- ggplot()+
  # add light contours
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-100, -200),
               size=c(0.3),
               colour="grey")+
  
  # add dark contours
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-500, -1000, -2000),
               size=c(0.5),
               colour="grey")+
  # add 0m contour
  geom_contour(data = bf,
               aes(x=x, y=y, z=z),
               breaks=c(0.5),
               size=c(0.5),
               colour="black")+
  # add points
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=LOCAL_TIME),
            colour = "black",
            stroke = .1, size = 4,
            alpha = 0.8, shape = 21)  +
  # configure projection and plot domain
  coord_map(xlim = lons, ylim = lats)  +
  #scale bar
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  ylab("")+xlab("")+
  theme_bw()

ggsave('/Users/kpitz/Projects/Maps/CN18F_time.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_time.svg')
p

```


```{r}
p <- ggplot()+
  # add light contours
  # add points
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=LOCAL_TIME),
            colour = "black",
            stroke = .1, size = 2,
            alpha = 0.8, shape = 21)  +
  # configure projection and plot domain
  coord_map(xlim = lons, ylim = lats)  +
  #scale bar
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  ylab("")+xlab("")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),
          legend.text = element_text(size = 10, colour = "black"),
          legend.title = element_text(face = "bold", size=10),
          legend.key = element_rect(fill = FALSE, colour = FALSE),
          legend.key.size = unit(0.5, "cm")
    )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))
  
p
  

ggsave('/Users/kpitz/Projects/Maps/CN18F_test_time.png')
p
```

```{r}
# make plot
p <- ggplot()+
  # add 50m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-50),
               size=c(0.3),
               colour="grey")+
  
  
  # add 100m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-100),
               size=c(0.3),
               colour="grey")+
  
  # add 150m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-150),
               size=c(0.3),
               colour="grey")+
  
  # add 200m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-200),
               size=c(0.3),
               colour="grey")+
  # add 300m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-300),
               size=c(0.3),
               colour="grey")+
  # add 400m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-400),
               size=c(0.3),
               colour="grey")+
  
  # add 500m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-500),
               size=c(0.5),
               colour="grey")+
  
  # add 1000m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-1000),
               size=c(0.5),
               colour="grey")+
  
  # add 2000m contour
  geom_contour(data = bf, 
               aes(x=x, y=y, z=z),
               breaks=c(-2000),
               size=c(0.5),
               colour="grey")+
  
  # add 0m contour
  geom_contour(data = bf,
               aes(x=x, y=y, z=z),
               breaks=c(0.5),
               size=c(0.5),
               colour="black")+
  
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),
               breaks=c(100)) +
  # add points
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=LOCAL_TIME),
            colour = "black",
            stroke = .2, size = 2,
            alpha = 1, shape = 21)+
  # geom_text(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=depth, label=SC),
  #           size=1, vjust=2.5, fontface = "bold") +

  # configure projection and plot domain
  coord_map(xlim = lons, ylim = lats)+
  
  #scale bar
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  ylab("")+xlab("")+
  guides(title = "Time", color = guide_legend(override.aes = list(size=5, shape=15))) +
  theme_bw()
ggsave('/Users/kpitz/Projects/Maps/CN18F_test_time.png')
p



```




## FINAL PLOTS with CONTOURS
```{r}
# DEPTH CONTOURS
test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m",
                               "300-400m","400-500m","500-1000m",
                               "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth.svg')
#GREYSCALE CONTOURS
test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  scale_fill_brewer(palette = "Greys",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m",
                               "300-400m","400-500m","500-1000m",
                               "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth_grey.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_contour_depth_grey.svg')

```

#line contours

```{r}
test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.6, breaks= c(5000,0,-5000)) +
  scale_fill_manual(values = c('darkgrey','white')) +
  geom_contour(data = bf,
               size=c(0.1),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-100,-200,-300,-400)) +
  geom_contour(data = bf,
               size=c(0.3),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-500,-1000, -2000, -3500)) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  labs(x="", y="") +
  theme_bw()


ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth.svg')
test
```

#color by diel cycle

```{r}
test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.6, breaks= c(5000,0,-5000)) +
  scale_fill_manual(values = c('darkgrey','white')) +
  geom_contour(data = bf,
               size=c(0.1),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-100,-200,-300,-400)) +
  geom_contour(data = bf,
               size=c(0.3),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-500,-1000, -2000, -3500)) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=fct_reorder(Diel, hour)),
            #colour = "black",fill='grey',
            stroke = 0.5, 
            size = 2,
            alpha = 1,
            shape=21) +
  scale_fill_brewer(palette = "Blues",name="Hour")+
  coord_map(xlim = lons, ylim = lats) +
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  labs(x="", y="") +
  theme_bw()

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth_diel.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth_diel.svg')




test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.6, breaks= c(5000,0,-5000)) +
  scale_fill_manual(values = c('darkgrey','white')) +
  geom_contour(data = bf,
               size=c(0.1),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-100,-200,-300,-400)) +
  geom_contour(data = bf,
               size=c(0.3),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-500,-1000, -2000, -3500)) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, size=Diel),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  labs(x="", y="") +
  theme_bw()

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth_diel.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth_diel.svg')



```


```{r}

test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.6, breaks= c(5000,0,-5000)) +
  scale_fill_manual(values = c('darkgrey','white')) +
  geom_contour(data = bf,
               size=c(0.1),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-100,-200,-300,-400)) +
  geom_contour(data = bf,
               size=c(0.3),
               aes(x=x, y=y, z=z),
               alpha=0.8, color='grey',
               breaks= c(-500,-1000, -2000, -3500)) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, size=Diel),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  labs(x="", y="") +
  theme_bw()

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth_diel.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth_diel.svg')











  
  
  geom_contour(data = bf,
               size=c(0.2),
               aes(x=x, y=y, z=z,color = stat(level)),
               alpha=0.8, 
               breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500))
test

test <- ggplot()+
  geom_contour(data = bf,
               size=c(0.2),
               colour="grey",
               aes(x=x, y=y, z=z,color = stat(z)),
               alpha=0.8, 
               breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
               #breaks= c(5000,0,-50,-75,-100,-150,-200,-300,-400,-500,-1000, -2000, -3500)) +
  # scale_colour_brewer(palette = "Greys",name="Depth", 
  #                     labels=c("0m","0-100m","100-200m","200-300m",
  #                              "300-400m","400-500m","500-1000m",
  #                              "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat),
            colour = "black",fill='grey',
            stroke = 0.5, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  labs(x="", y="") +
  theme_bw()

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth.png')
ggsave('/Users/kpitz/Projects/Maps/CN18F_lines_depth.svg')
```









```{r}

test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m",
                               "300-400m","400-500m","500-1000m",
                               "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, label=SC),
            colour = "black",fill='grey',
            stroke = .2, size = 2,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats) +
  labs(x="", y="")

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_test.png')






test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500))+
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m","300-400m","400-500m","500-1000m","1000-2000m","2000-3500m")) +
  ylab("") +
  xlab("") +
  coord_map(xlim = lons, ylim = lats)

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_test.png')
test + geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, label=SC),
            #colour = "black",fill='grey',
            stroke = .2, size = 2,
            alpha = 1, shape = 21)+
  geom_text(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=depth, label=SC),
            size=1, vjust=2.5, fontface = "bold")
ggsave('/Users/kpitz/Projects/Maps/CN18F_test_labeled.png')











test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500))+
  # scale_fill_brewer(palette = "Blues",name="Depth", 
  #                     labels=c("0m","0-100m","100-200m","200-300m","300-400m","400-500m","500-1000m","1000-2000m","2000-3500m")) +
  ylab("") +
  xlab("") +
  coord_map(xlim = lons, ylim = lats) +
  # add points
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, label=SC),
            colour = "black",fill='grey',
            stroke = .2, size = 2,
            alpha = 1, shape = 21)+
  geom_text(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, fill=depth, label=SC),
            size=1, vjust=2.5, fontface = "bold")

test
ggsave('/Users/kpitz/Projects/Maps/CN18F_test.png')


test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z),alpha=0.8, breaks= c(5000,0,-100,-200,-300,-400,-500,-1000, -2000, -3500)) +
  scale_fill_brewer(palette = "Blues",name="Depth", 
                      labels=c("0m","0-100m","100-200m","200-300m",
                               "300-400m","400-500m","500-1000m",
                               "1000-2000m","2000-3500m")) +
  geom_point(data = pts, aes(x = SAMPLING_dec_long, y = SAMPLING_dec_lat, label=SC),
            colour = "black",fill='grey',
            stroke = .2, size = 1,
            alpha = 1, shape = 21) +
  coord_map(xlim = lons, ylim = lats)

test


#SCRAP

test <- ggplot()+
  geom_contour_filled(data = bf,
               aes(x=x, y=y, z=z))+
  scale_fill_brewer(palette = "Blues")
test
+
  #labs(x="Longitude", y="Latitude")+
# configure projection and plot domain
  coord_map(xlim = lons, ylim = lats)+
  
  #scale bar
  scalebar(data = df, dist = 10, dist_unit = "km", st.size=3, height=0.02,
             transform = TRUE, model = "WGS84", location= "topright") +
  # formatting
  ylab("")+xlab("")+
  theme_bw()
ggsave('/Users/kpitz/Projects/Maps/CN18F_test.png')
test

```













