---
title: "QIIME2- deicode"
author: "Pitz K"
date: "11/29/2021"
output: html_document
---

# Load libraries
```{r}
#load libraries
library(tidyverse) #includes multiple libraries
library(lubridate) #for date modifications

```

# Set Location to save results
```{r}
marker = '12S'
prefix = 'CN19S'
data_directory = "../data/filtered_seq_data/"
# Set directory to save plots
plot_dir <- '../figures/RPCA/'
results_directory <- '../Qiime_Results/'
```

# load in data
```{r}
#ASV table
print('ASV table')
file = paste(prefix,"_",marker,"_otu_filtered.csv", sep='')
filepath = paste(data_directory, file, sep='')
print(filepath)
otu.c <- read_csv(filepath) %>% rename_with(.cols = 1, ~"ASV")

#taxa table
print('taxa table')
file = paste(prefix,"_",marker,"_taxa_filtered.csv", sep='')
filepath = paste(data_directory, file, sep='')
print(filepath)
tax.c <- read_csv(filepath) %>% rename_with(.cols = 1, ~"ASV")

#metadata table
print('metadata table')
file = paste(prefix,"_",marker,"_meta_filtered.csv", sep='')
filepath = paste(data_directory, file, sep='')
print(filepath)
samp.c <- read_csv(filepath) %>% rename('SampleID' = 'sample_name')

#OTU table long format with percent total reads
potu.c <- otu.c %>%
  tidyr::pivot_longer( -ASV, names_to ='SampleID',values_to = 'reads' ) %>%
  group_by(SampleID) %>%
  mutate(per_tot = reads / sum(reads) *100) %>%
  ungroup() %>%
  arrange(-reads)
head(potu.c)
```




# Export tables for DEICODE
```{r}
#ASV table
#"#OTUID"
filename = paste(results_directory, "Qiime2_asv.tsv", sep='')
#check filename
print(filename)

otu.c %>%
  rename('#OTUID' = ASV) %>%
  write_delim(filename, delim="\t")

#Taxa table
#"#OTUID"
filename = paste(results_directory, "Qiime2_taxa.tsv", sep='')
#check filename
print(filename)

tax.c %>%
  rename('#OTUID' = ASV) %>%
  write_delim(filename, delim="\t")
  
#Metadata Table
#SampleID
filename = paste(results_directory, "Qiime2_meta.tsv", sep='')
#check filename
print(filename)

samp.c %>%
  select(SampleID,SAMPLING_cruise, depth ) %>%
  rename('#SampleID' = SampleID) %>%
  write_delim(filename, delim="\t")

```


## DEICODE PCA

# CHANGE PATH BELOW TO CD TO CORRECT DIRECTORY!!

```{bash engine.opts='-l'}
# move into the directory where you are going to run the DEICODE script
cd /Users/kpitz/github/MBARI-BOG/CN19S_12S/Qiime_Results
pwd

# Activate the conda qiime2 enviroment - check version
conda activate qiime2-2021.11

#Make biom file
biom convert -i ./Qiime2_asv.tsv -o table.from_txt_json.biom --table-type="OTU table" --to-json
#add metadata files to biom file - change the merged_tax_table_for_biomm.txt and _merged_for_biom.txt files
biom add-metadata -i table.from_txt_json.biom -o table.w_md.biom --observation-metadata-fp Qiime2_taxa.tsv --sample-metadata-fp Qiime2_meta.tsv

#import into Qiime2 - Change output file
qiime tools import \
--input-path table.w_md.biom \
--output-path Project.biom.qza \
--type FeatureTable[Frequency]

#run DEICODE - change input table
qiime deicode rpca \
--i-table Project.biom.qza \
--p-n-components 3 \
--p-min-feature-count 20 \
--p-min-sample-count 500 \
--o-biplot ordination.qza \
--o-distance-matrix distance.qza

## Create biplot - change metadata files
qiime emperor biplot \
--i-biplot ordination.qza \
--m-sample-metadata-file Qiime2_meta.tsv \
--m-feature-metadata-file Qiime2_taxa.tsv \
--o-visualization biplot.qzv \
--p-number-of-features 8



```



# PLOT


#make seasonal variables
```{r}
library(lubridate)
meta <- samp.c %>% 
  mutate(time = mdy_hm(local_time)) %>%
  mutate(time_since = as.numeric(time)) %>%
  mutate(ESP = case_when(str_detect(SampleID, 'SC')==TRUE ~'ESP',
                         str_detect(SampleID, 'Bongo')==TRUE ~'Bongo',
                         TRUE~'CTD')) %>%
  mutate(month =  month(time)) %>%
  mutate(day =  day(time)) %>%
  mutate(year =  year(time)) %>%
  mutate(jday = yday(time)) %>%
  mutate(month_char = as.character(month)) %>%
  mutate(year_char = as.character(year)) %>%
  mutate(depth_bin = case_when(depth <=50 ~ "0-50m",
                               depth >50 & depth <=100 ~ "50-100m",
                               depth >100 & depth <=200 ~ "100-200m",
                               depth >200 & depth <=300 ~ "200-300m",
                               depth >300 & depth <=400 ~ "300-400m",
                               depth >400 & depth <=500 ~ "400-500m",
                               depth >400 & depth <=600 ~ "500-600m",
                               depth >600 & depth <=750 ~ "600-750m", TRUE ~ "unknown"
                               )) 
```

```{r}
library(magrittr)
#project_meta %<>% rename(SampleID=sample_name)
```

#import data
```{r}
library(qiime2R)

#Import Qiime2 Results
file = paste(results_directory,"ordination.qza",sep="")
print(file)
pco<-read_qza(file)
pco$uuid
#look at data
head(pco$data$ProportionExplained)
pco$data$Vectors[1:5, 1:4]

#create proportion explained labels
label.PC1 <- paste("PC1: ", round(pco$data$ProportionExplained$PC1, 3)*100,"%")
label.PC1
label.PC2 <- paste("PC2: ", round(pco$data$ProportionExplained$PC2, 3)*100,"%")
label.PC2
label.PC3 <- paste("PC3: ", round(pco$data$ProportionExplained$PC3, 3)*100,"%")
label.PC3

#Join with sample data
pcscores <- left_join(pco$data$Vectors, meta, by="SampleID")

#format loading scores
loadings <- as.data.frame(pco$data$Species)
loadings$ASV <- loadings$FeatureID

#join on OTU, adding taxa info
loadings <- left_join(loadings, tax.c, by="ASV")

#export pcscores
file = paste(results_directory, "pcscores_",marker,"_Dada2_Qiime2.csv",sep="")
print(file)
write.csv(pcscores, file)
file = paste(results_directory, "loadings_",marker,"_Dada2_Qiime2.csv",sep="")
print(file)
write.csv(loadings, file)
pcscores[1:5, 1:9]  #long because of sample data
head(loadings)
```

#Plot RPCA

```{r}
library(RColorBrewer)
library(viridis)

# by mean depth class
p <- pcscores %>%
  group_by(depth_bin) %>%
  mutate(mPC1 = mean(PC1)) %>%
  mutate(mPC2 = mean(PC2)) %>%
  ungroup() %>%
  ggplot(aes(PC1,PC2,color=fct_reorder(depth_bin ,depth))) +
  geom_point(size=3, alpha=0.6, shape=16) +
  geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC1 , y=label.PC2, colour = "Depth Range" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC1PC2_mean_DepthRange.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

```

# Diel

```{r}
p <- pcscores %>%
  #group_by(depth_bin, diel) %>%
  #mutate(mPC1 = mean(PC1)) %>%
  #mutate(mPC2 = mean(PC2)) %>%
  #ungroup() %>%
  ggplot(aes(PC1,PC2,color=diel)) +
  geom_point(size=3, alpha=0.6, shape=16) #+
  #geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC1 , y=label.PC2, colour = "Diel" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC1PC2_diel.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

```



# Run for a limited series of samples:

# Limit by Taxonomy:
```{r}
#limit by taxonomy
#myctophiidae

# Set directory to save plots
plot_dir <- '../figures/RPCA_lim/'
results_directory <- '../Qiime_Results/Qiime_Results_lim/'

#Taxa table
#"#OTUID"
filename = paste(results_directory, "Qiime2_taxa.tsv", sep='')
#check filename
print(filename)

taxa_new <- tax.c %>%
  filter(Family!='Engraulidae') %>%
  filter(Family!='Merlucciidae')


taxa_new %>%
  rename('#OTUID' = ASV) %>%
  write_delim(filename, delim="\t")

#ASV table
#"#OTUID"
filename = paste(results_directory, "Qiime2_asv.tsv", sep='')
#check filename
print(filename)

otu_new <- left_join(taxa_new, potu.c) %>%
  select(ASV, SampleID, reads) %>%
  pivot_wider(id_cols=ASV, names_from = SampleID, values_from = reads) %>%
  mutate(sum = rowSums(across(where(is.numeric)))) %>%
  filter(sum>0) %>%
  select(-sum)

otu_new %>%
  rename('#OTUID' = ASV) %>%
  write_delim(filename, delim="\t")


#Metadata Table
#SampleID
filename = paste(results_directory, "Qiime2_meta.tsv", sep='')
#check filename
print(filename)

samp.c %>%
  select(SampleID,SAMPLING_cruise, depth ) %>%
  #filter(depth<=450) %>%
  #filter(depth>=0) %>%
  rename('#SampleID' = SampleID) %>%
  write_delim(filename, delim="\t")

```

# Limit by Taxonomy and Depth:

```{r}
#limit by taxonomy
#myctophiidae

# Set directory to save plots
plot_dir <- '../figures/RPCA_lim/'
results_directory <- '../Qiime_Results/Qiime_Results_lim/'

# #Taxa table
# #"#OTUID"
# filename = paste(results_directory, "Qiime2_taxa.tsv", sep='')
# #check filename
# print(filename)

taxa_new <- tax.c %>%
  filter(Family!='Engraulidae') %>%
  filter(Family!='Merlucciidae')


# taxa_new %>%
#   rename('#OTUID' = ASV) %>%
#   write_delim(filename, delim="\t")

#ASV table
#"#OTUID"
filename = paste(results_directory, "Qiime2_asv.tsv", sep='')
#check filename
print(filename)

otu_new <- left_join(taxa_new, potu.c) %>%
  select(ASV, SampleID, reads) %>%
  pivot_wider(id_cols=ASV, names_from = SampleID, values_from = reads) %>%
  mutate(sum = rowSums(across(where(is.numeric)))) %>%
  filter(sum>0) %>%
  select(-sum)

#OTU table long format with percent total reads
potu_new <- otu_new %>%
  tidyr::pivot_longer( -ASV, names_to ='SampleID',values_to = 'reads' ) %>%
  group_by(SampleID) %>%
  mutate(per_tot = reads / sum(reads) *100) %>%
  ungroup() %>%
  arrange(-reads)
head(potu_new)

otu_new <- left_join(meta, potu_new) %>%
  filter(depth<600) %>%
  filter(depth>=0) %>%
  select(ASV, SampleID, reads) %>%
  pivot_wider(id_cols=ASV, names_from = SampleID, values_from = reads) %>%
  rename('#OTUID' = ASV) %>%
  mutate(sum = rowSums(across(where(is.numeric)))) %>%
  filter(sum>0) %>%
  select(-sum) %>%
  write_delim(filename, delim="\t")



#Taxa table
#"#OTUID"
filename = paste(results_directory, "Qiime2_taxa.tsv", sep='')
#check filename
print(filename)

taxa_new <- potu_new %>%
  left_join(taxa_new) %>%
  select(-SampleID, -reads) %>%
  distinct(ASV, .keep_all=TRUE) %>%
  rename('#OTUID' = ASV) %>%
  write_delim(filename, delim="\t")

  
#Metadata Table
#SampleID
filename = paste(results_directory, "Qiime2_meta.tsv", sep='')
#check filename
print(filename)

samp.c %>%
  select(SampleID,SAMPLING_cruise, depth ) %>%
  filter(depth<600) %>%
  filter(depth>=0) %>%
  rename('#SampleID' = SampleID) %>%
  write_delim(filename, delim="\t")

```


# Limit by depth
```{r}
# Set directory to save plots
plot_dir <- '../figures/RPCA_lim/'
results_directory <- '../Qiime_Results/Qiime_Results_lim/'

#filter and export tables
#try just samples <300m

#ASV table
#"#OTUID"
filename = paste(results_directory, "Qiime2_asv.tsv", sep='')
#check filename
print(filename)

otu_new <- left_join(meta, potu.c) %>%
  filter(depth<=450) %>%
  filter(depth>=0) %>%
  select(ASV, SampleID, reads) %>%
  pivot_wider(id_cols=ASV, names_from = SampleID, values_from = reads) %>%
  rename('#OTUID' = ASV) %>%
  mutate(sum = rowSums(across(where(is.numeric)))) %>%
  filter(sum>0) %>%
  select(-sum) %>%
  write_delim(filename, delim="\t")
  
potu_new <- otu_new %>%
  rename(ASV = '#OTUID') %>%
  pivot_longer(-ASV,names_to="SampleID", values_to ="reads")

#Taxa table
#"#OTUID"
filename = paste(results_directory, "Qiime2_taxa.tsv", sep='')
#check filename
print(filename)

taxa_new <- potu_new %>%
  left_join(tax.c) %>%
  select(-SampleID, -reads) %>%
  distinct(ASV, .keep_all=TRUE) %>%
  rename('#OTUID' = ASV) %>%
  write_delim(filename, delim="\t")

  
#Metadata Table
#SampleID
filename = paste(results_directory, "Qiime2_meta.tsv", sep='')
#check filename
print(filename)

samp.c %>%
  select(SampleID,SAMPLING_cruise, depth ) %>%
  filter(depth<=450) %>%
  filter(depth>=0) %>%
  rename('#SampleID' = SampleID) %>%
  write_delim(filename, delim="\t")
```

### DEICODE PCA

### CHANGE PATH BELOW TO CD TO CORRECT DIRECTORY!!

```{bash engine.opts='-l'}
# move into the directory where you are going to run the DEICODE script
cd /Users/kpitz/github/MBARI-BOG/CN19S_12S/Qiime_Results/Qiime_Results_lim
pwd

# Activate the conda qiime2 enviroment - check version
conda activate qiime2-2021.11

#Make biom file
biom convert -i ./Qiime2_asv.tsv -o table.from_txt_json.biom --table-type="OTU table" --to-json
#add metadata files to biom file - change the merged_tax_table_for_biomm.txt and _merged_for_biom.txt files
biom add-metadata -i table.from_txt_json.biom -o table.w_md.biom --observation-metadata-fp Qiime2_taxa.tsv --sample-metadata-fp Qiime2_meta.tsv

#import into Qiime2 - Change output file
qiime tools import \
--input-path table.w_md.biom \
--output-path Project.biom.qza \
--type FeatureTable[Frequency]

#run DEICODE - change input table
qiime deicode rpca \
--i-table Project.biom.qza \
--p-n-components 3 \
--p-min-feature-count 20 \
--p-min-sample-count 500 \
--o-biplot ordination.qza \
--o-distance-matrix distance.qza

## Create biplot - change metadata files
qiime emperor biplot \
--i-biplot ordination.qza \
--m-sample-metadata-file Qiime2_meta.tsv \
--m-feature-metadata-file Qiime2_taxa.tsv \
--o-visualization biplot.qzv \
--p-number-of-features 8



```


### PLOT


### make seasonal variables
```{r}
library(lubridate)
meta <- samp.c %>% 
  mutate(time = mdy_hm(local_time)) %>%
  mutate(time_since = as.numeric(time)) %>%
  mutate(ESP = case_when(str_detect(SampleID, 'SC')==TRUE ~'ESP',
                         str_detect(SampleID, 'Bongo')==TRUE ~'Bongo',
                         TRUE~'CTD')) %>%
  mutate(month =  month(time)) %>%
  mutate(day =  day(time)) %>%
  mutate(year =  year(time)) %>%
  mutate(jday = yday(time)) %>%
  mutate(month_char = as.character(month)) %>%
  mutate(year_char = as.character(year)) %>%
  mutate(depth_bin = case_when(depth <=50 ~ "0-50m",
                               depth >50 & depth <=100 ~ "50-100m",
                               depth >100 & depth <=200 ~ "100-200m",
                               depth >200 & depth <=300 ~ "200-300m",
                               depth >300 & depth <=400 ~ "300-400m",
                               depth >400 & depth <=500 ~ "400-500m",
                               depth >400 & depth <=600 ~ "500-600m",
                               depth >600 & depth <=750 ~ "600-750m", TRUE ~ "unknown"
                               )) 
```

```{r}
library(magrittr)
#project_meta %<>% rename(SampleID=sample_name)
```

###import data
```{r}
library(qiime2R)

#Import Qiime2 Results
file = paste(results_directory,"ordination.qza",sep="")
print(file)
pco<-read_qza(file)
pco$uuid
#look at data
head(pco$data$ProportionExplained)
pco$data$Vectors[1:5, 1:4]

#create proportion explained labels
label.PC1 <- paste("PC1: ", round(pco$data$ProportionExplained$PC1, 3)*100,"%")
label.PC1
label.PC2 <- paste("PC2: ", round(pco$data$ProportionExplained$PC2, 3)*100,"%")
label.PC2
label.PC3 <- paste("PC3: ", round(pco$data$ProportionExplained$PC3, 3)*100,"%")
label.PC3

#Join with sample data
pcscores <- left_join(pco$data$Vectors, meta, by="SampleID")

#format loading scores
loadings <- as.data.frame(pco$data$Species)
loadings$ASV <- loadings$FeatureID

#join on OTU, adding taxa info
loadings <- left_join(loadings, tax.c, by="ASV")

#export pcscores
file = paste(results_directory, "pcscores_",marker,"_Dada2_Qiime2.csv",sep="")
print(file)
write.csv(pcscores, file)
file = paste(results_directory, "loadings_",marker,"_Dada2_Qiime2.csv",sep="")
print(file)
write.csv(loadings, file)
pcscores[1:5, 1:9]  #long because of sample data
head(loadings)
```

###Plot RPCA

```{r}
library(RColorBrewer)
library(viridis)

# by mean depth class
p <- pcscores %>%
  group_by(depth_bin) %>%
  mutate(mPC1 = mean(PC1)) %>%
  mutate(mPC2 = mean(PC2)) %>%
  ungroup() %>%
  ggplot(aes(PC1,PC2,color=fct_reorder(depth_bin ,depth))) +
  geom_point(size=3, alpha=0.6, shape=16) +
  geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC1 , y=label.PC2, colour = "Depth Range" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC1PC2_mean_DepthRange.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

```

### Diel

```{r}
p <- pcscores %>%
  #group_by(depth_bin, diel) %>%
  #mutate(mPC1 = mean(PC1)) %>%
  #mutate(mPC2 = mean(PC2)) %>%
  #ungroup() %>%
  ggplot(aes(PC1,PC2,color=diel)) +
  geom_point(size=3, alpha=0.6, shape=16) #+
  #geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC1 , y=label.PC2, colour = "Diel" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC1PC2_diel.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

p <- pcscores %>%
  #group_by(depth_bin, diel) %>%
  #mutate(mPC1 = mean(PC1)) %>%
  #mutate(mPC2 = mean(PC2)) %>%
  #ungroup() %>%
  ggplot(aes(PC2,PC3,color=diel)) +
  geom_point(size=3, alpha=0.6, shape=16) #+
  #geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC2 , y=label.PC3, colour = "Diel" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC2PC3_diel.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

```

### PlateID

```{r}
p <- pcscores %>%
  #group_by(depth_bin, diel) %>%
  #mutate(mPC1 = mean(PC1)) %>%
  #mutate(mPC2 = mean(PC2)) %>%
  #ungroup() %>%
  ggplot(aes(PC1,PC2,color=PlateID)) +
  geom_point(size=3, alpha=0.6, shape=16) #+
  #geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC1 , y=label.PC2, colour = "PlateID" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC1PC2_PlateID.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

```
# STATION

```{r}
p <- pcscores %>%
  #group_by(depth_bin, diel) %>%
  #mutate(mPC1 = mean(PC1)) %>%
  #mutate(mPC2 = mean(PC2)) %>%
  #ungroup() %>%
  ggplot(aes(PC1,PC2,color=SAMPLING_station)) +
  geom_point(size=3, alpha=0.6, shape=16) #+
  #geom_point(size=7, shape=16, aes(x=mPC1, y=mPC2))

p+labs(x=label.PC1 , y=label.PC2, colour = "PlateID" )+ ggtitle(marker)+
  #theme_minimal()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        legend.text = element_text(size = 10, colour = "black"),
        legend.title = element_text(face = "bold", size=12),
        legend.key = element_rect(fill = FALSE, colour = FALSE),
        legend.key.size = unit(0.1,"line")
  )+ guides(color = guide_legend(override.aes = list(size=5, shape=15)))

filename = paste(plot_dir, 'RPCA_',marker,'_PC1PC2_station.png', sep='')
filename
ggsave(filename,height = 5, width =7, units = 'in')

```




# PC Value through time

```{r}
#Plot PC values through time

p <- pcscores %>%
  mutate(local_time = mdy_hm(local_time)) %>%
  ggplot(aes(local_time,PC1,color=diel, shape=ESP)) +
  geom_point(size=3, alpha=0.6) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

p

```

#Ait distance through time
```{r}
# Ait distance:

file = paste(results_directory,"distance.qza",sep="")
print(file)
ait <-read_qza(file)
ait
aitmat <- as.matrix(ait$data)
aitdist <- as.dist(aitmat)

```
```{r}
#transform aitchenson distance matrix into format for 
#plotting distance between depths
# get into long format to get distance from sample to sample

ait_tib <-as_tibble(aitmat,rownames = "SampleID") %>%
  pivot_longer(-SampleID,names_to = "SampleID2", values_to = "distance")

# add in metadata for both 1 and 2:
lim_meta <- select(meta,c('SampleID','depth_bin', 'depth', 'diel', 'day', 'time'))
ait_tib %<>% left_join(lim_meta, by="SampleID")
ait_tib %<>% left_join(lim_meta %>% mutate(SampleID2 = SampleID), by="SampleID2", suffix= (c("1","2"))) %>%
  select(-SampleID22) %>%
  mutate(interaction_type = paste(diel1,'-',diel2),sep='')

```


```{r}
# one sample to the next:
p <- ait_tib %>%
  arrange(time2) %>%
  arrange(time1) %>%
  filter(time2>time1) %>%
  distinct(SampleID1, .keep_all=TRUE) %>%
  ggplot(aes(time1,distance)) +
  geom_point(size=3, alpha=0.6) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

p



```

### cluster
```{r}
library(ggdendro)
aitclust <- hclust(aitdist, method= "ward.D2")
plot(aitclust)
aitdend <- as.dendrogram(aitclust, hang = -1, lwd = 3, lty = 3, sub = "")
#dend_cols <- select(samp.c,c('SampleID','date'))
plot(aitdend)


#Can plot with ggplot2

dendr <- dendro_data(aitclust, type="rectangle") 

#Define cluster based on similarity percent - good for plotting
clust <- cutree(aitclust, h = 6)               # find 'cut' clusters (k) or choose level (h) numeric scalar or vector with heights where the tree should be cut.
clust2 <- cutree(aitclust, h = 2)
clust3 <- cutree(aitclust, h = 10)  
clust4 <- cutree(aitclust, h = 16)  

clust.df <- data.frame(label = names(clust), cluster_6 = clust, cluster_2 = clust2, cluster_10 = clust3, cluster_16 = clust4)
sapply(clust.df, mode)
clust.df$label <- as.character(clust.df$label)
clust.df <- clust.df[order(clust.df$label),]

#join sample data with cluster df and simprofCLUSTERS df:
tree_scores <- as_tibble(clust.df) %>% rename(SampleID = label) %>% left_join(pcscores, by='SampleID')
tree_data <- as_tibble(dendr$labels) %>% 
  rename(SampleID = label) %>% 
  left_join(tree_scores, by='SampleID') %>% 
  mutate(local_time = mdy_hm(local_time)) %>%
  arrange(depth_bin)

# In PCA space:
tree_data %>%ggplot(aes(x= PC1, y=PC2, color=cluster_16))+
  geom_point()
tree_data %>%ggplot(aes(x= PC1, y=PC2, color=cluster_10))+
  geom_point()
tree_data %>%ggplot(aes(x= PC1, y=PC2, color=cluster_2))+
  geom_point()

#By depth_bin
ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=fct_reorder(depth_bin,depth)),alpha=1, size=1)+
  geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse(expand=c(.5, 0)) + 
  scale_color_brewer(palette='Set1')+
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())

filename = paste(plot_dir, 'Aitdist_',marker,'_hclust_depth.png', sep='')
filename
ggsave(filename,height = 4, width =6, units = 'in')

#By day
library(viridis)
ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=local_time),alpha=1, size=1)+
  geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse(expand=c(.5, 0)) + 
  scale_color_viridis(option="turbo")+
  #scale_color_brewer(palette='Set1')+
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())

filename = paste(plot_dir, 'Aitdist_',marker,'_hclust_day.png', sep='')
filename
ggsave(filename,height = 4, width =6, units = 'in')

#By depth
ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1)+
  geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse(expand=c(.5, 0)) + 
  scale_color_viridis(option="turbo")+
  #scale_color_brewer(palette='Set1')+
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())


cluster_plot <- ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1)+
  geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse(expand=c(.5, 0)) + 
  scale_color_viridis(option="turbo")+
  #scale_color_brewer(palette='Set1')+
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())
```

# For Taxonomy:

```{r}
#bar plots

potu_new2 <- otu_new %>%
  tidyr::pivot_longer( -ASV, names_to ='SampleID',values_to = 'reads' ) %>%
  group_by(SampleID) %>%
  mutate(per_tot = reads / sum(reads) *100) %>%
  ungroup() %>%
  arrange(-reads)
head(potu_new2)


taxa_level = sym('Genus')
top_taxa <- potu_new2 %>%
  full_join(taxa_new ) %>%
  # filter(!!taxa_level != 'Unknown') %>%
  # filter(!!taxa_level !='no_hit') %>%
  filter(!!taxa_level !='unassigned') %>%
  # filter(!!taxa_level !='unknown') %>%
  # filter(!!taxa_level !='s_') %>%
  # filter(!!taxa_level !='g_') %>%
  unite(taxa_label, Class, Order, Family, Genus, sep='_') %>%
  group_by(taxa_label) %>%
  mutate(sum_per_tot = sum(per_tot)) %>%
  distinct(taxa_label,.keep_all = TRUE ) %>%
  arrange(-sum_per_tot) %>%
  select(taxa_label, sum_per_tot) %>%
  #print(n = Inf) %>%
  ungroup() %>%
  select(taxa_label, sum_per_tot) %>%
  top_n(20)

# assign text colour
library(ggthemes)
textcol <- "grey40"
print("Begin plotting...")
bp_top <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  inner_join(taxa_new ,  by = c("ASV")) %>%  #join with taxonomy
  #make taxa label
  unite(taxa_label, Class, Order, Family, Genus, sep='_') %>%
  right_join(top_taxa) %>% #limit to top taxa
  ggplot(aes(x = fct_reorder(SampleID, x), y = per_tot)) +
  geom_bar(stat = "identity", aes(fill = taxa_label))+
  scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="Percent Total Reads")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    axis.text.y=element_text(size=6,colour=textcol),
    axis.title.y = element_text(size=6),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())

filename = paste(plot_dir, marker,'_top20',taxa_level,'_bar_comp.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

#plot cluster groups?
bp_side <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  ggplot(aes(x = fct_reorder(SampleID, x), y = 1)) +
  geom_bar(stat = "identity", aes(fill = cluster_6))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="clust")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=2)) +
  coord_flip() +
  theme(
    #legend
    legend.position="bottom",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=8,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=8,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())

filename = paste(plot_dir, marker,'_cluster6_.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

# bp_side2 <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
#   ggplot(aes(x = fct_reorder(SampleID, x), y = 1)) +
#   geom_bar(stat = "identity", aes(fill = depth))+
#   #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
#   labs(x="",y="Total Reads")+
#   theme_minimal() +
#   guides(fill=guide_legend(ncol=1)) +
#   coord_flip() +
#   theme(
#     #legend
#     legend.position="right",legend.direction="vertical",
#     legend.text=element_text(colour=textcol,size=8,face="bold"),
#     legend.key.height=grid::unit(0.3,"cm"),
#     legend.key.width=grid::unit(0.3,"cm"),
#     legend.title=element_text(colour=textcol,size=8,face="bold"),
#     axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=5,colour=textcol),
#     #axis.text.x=element_text(size=7,colour=textcol),
#     #axis.text.y=element_text(size=6,colour=textcol),
#     #axis.title.y = element_text(size=6),
#     axis.line.y=element_blank(),
#     axis.ticks.y=element_blank(),
#     axis.text.y=element_blank(),
#     axis.title.y=element_blank(),
#     plot.background=element_blank(),
#     panel.border=element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.grid.major = element_line(size = .25),
#     plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
#     plot.title=element_blank())


bp_side2 <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  ggplot(aes(x = fct_reorder(SampleID, x), y = depth)) +
  #geom_bar(stat = "identity", aes(fill = depth))+
  geom_point(aes(shape=ESP,color = diel))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="depth(m)")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())


bp_side3 <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  #mutate(local_time = mdy_hms(local_time)) %>%
  ggplot(aes(x = fct_reorder(SampleID, x), y = local_time)) +
  #geom_bar(stat = "identity", aes(fill = depth))+
  geom_point(aes(shape=ESP,color = diel))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="time")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())



#cluster plot  
cluster_plot <- ggplot() + 
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1)+
  #geom_bar(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1) +
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  #geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  #geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse() + 
  scale_color_viridis(option="viridis")+
  #scale_color_brewer(palette='Set1')+
  theme(axis.line=element_blank(),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        axis.title=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())

# library(gridExtra)
# grid.arrange(cluster_plot, bp_top, ncol=2)
# 
# gA <- ggplotGrob(A)
# gB <- ggplotGrob(B)
# maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5])
# gA$widths[2:5] <- as.list(maxWidth)
# gB$widths[2:5] <- as.list(maxWidth)
# grid.arrange(gA, gB, ncol=1)
#   
# 
# gA <- ggplotGrob(bp_side)
# gB <- ggplotGrob(bp_top)
# grid::grid.newpage()
# grid::grid.draw(rbind(gA, gB))

library(cowplot)
#plot_grid(bp_side+guides(fill="none"), bp_top+guides(fill="none"), labels = c('A', 'B'), label_size = 12)

plot_grid(cluster_plot+guides(fill="none", color="none"),bp_side+guides(fill="none"),bp_side2+guides(fill="none"), bp_top, label_size = 6, align = "h", ncol=4, rel_widths=c(2,0.5,1,5))

filename = paste(plot_dir, marker,'_cluster_top20_depth.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')
```
# Taxonomy and depth
```{r}
taxa_new <- taxa_new %>% rename(ASV=`#OTUID`) %>% select(-per_tot)
taxa_new <- taxa_new %>% select(-per_tot)

```


```{r}
#bar plots

taxa_level = sym('Genus')
top_taxa <- potu_new %>%
  full_join(taxa_new ) %>%
  # filter(!!taxa_level != 'Unknown') %>%
  # filter(!!taxa_level !='no_hit') %>%
  filter(!!taxa_level !='unassigned') %>%
  # filter(!!taxa_level !='unknown') %>%
  # filter(!!taxa_level !='s_') %>%
  # filter(!!taxa_level !='g_') %>%
  unite(taxa_label, Class, Order, Family, Genus, sep='_') %>%
  group_by(taxa_label) %>%
  mutate(sum_per_tot = sum(per_tot)) %>%
  distinct(taxa_label,.keep_all = TRUE ) %>%
  arrange(-sum_per_tot) %>%
  select(taxa_label, sum_per_tot) %>%
  #print(n = Inf) %>%
  ungroup() %>%
  select(taxa_label, sum_per_tot) %>%
  top_n(20)

# assign text colour
library(ggthemes)
textcol <- "grey40"
print("Begin plotting...")
bp_top <- inner_join(potu_new, tree_data,  by = c("SampleID")) %>% #join with metadata
  inner_join(taxa_new ,  by = c("ASV")) %>%  #join with taxonomy
  #make taxa label
  unite(taxa_label, Class, Order, Family, Genus, sep='_') %>%
  right_join(top_taxa) %>% #limit to top taxa
  ggplot(aes(x = fct_reorder(SampleID, x), y = per_tot)) +
  geom_bar(stat = "identity", aes(fill = taxa_label))+
  scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="Percent Total Reads")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    axis.text.y=element_text(size=6,colour=textcol),
    axis.title.y = element_text(size=6),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())

filename = paste(plot_dir, marker,'_top20',taxa_level,'_bar_comp.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

#plot cluster groups?
bp_side <- inner_join(potu_new, tree_data,  by = c("SampleID")) %>% #join with metadata
  ggplot(aes(x = fct_reorder(SampleID, x), y = 1)) +
  geom_bar(stat = "identity", aes(fill = cluster_6))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="clust")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=2)) +
  coord_flip() +
  theme(
    #legend
    legend.position="bottom",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=8,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=8,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())

filename = paste(plot_dir, marker,'_cluster6_.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')


bp_side2 <- inner_join(potu_new, tree_data,  by = c("SampleID")) %>% #join with metadata
  ggplot(aes(x = fct_reorder(SampleID, x), y = depth)) +
  #geom_bar(stat = "identity", aes(fill = depth))+
  geom_point(aes(shape=ESP,color = diel))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="depth(m)")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())


bp_side3 <- inner_join(potu_new, tree_data,  by = c("SampleID")) %>% #join with metadata
  #mutate(local_time = mdy_hms(local_time)) %>%
  ggplot(aes(x = fct_reorder(SampleID, x), y = local_time)) +
  #geom_bar(stat = "identity", aes(fill = depth))+
  geom_point(aes(shape=ESP,color = diel))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="time")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())



#cluster plot  
cluster_plot <- ggplot() + 
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1)+
  #geom_bar(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1) +
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  #geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  #geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse() + 
  scale_color_viridis(option="viridis")+
  #scale_color_brewer(palette='Set1')+
  theme(axis.line=element_blank(),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        axis.title=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())

library(cowplot)
#plot_grid(bp_side+guides(fill="none"), bp_top+guides(fill="none"), labels = c('A', 'B'), label_size = 12)

plot_grid(cluster_plot+guides(fill="none", color="none"),bp_side+guides(fill="none"),bp_side2+guides(fill="none"), bp_top, label_size = 6, align = "h", ncol=4, rel_widths=c(2,0.5,1,5))

filename = paste(plot_dir, marker,'_cluster_top20_depth.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

filename = paste(plot_dir, marker,'_cluster_top20_depth.svg', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

```


# For Depth

```{r}
#bar plots

potu_new2 <- potu_new %>%
  #tidyr::pivot_longer( -ASV, names_to ='SampleID',values_to = 'reads' ) %>%
  group_by(SampleID) %>%
  mutate(per_tot = reads / sum(reads) *100) %>%
  ungroup() %>%
  arrange(-reads)
head(potu_new2)


taxa_level = sym('Genus')
top_taxa <- potu_new2 %>%
  full_join(taxa_new %>% rename(ASV = `#OTUID`)) %>%
  # filter(!!taxa_level != 'Unknown') %>%
  # filter(!!taxa_level !='no_hit') %>%
  filter(!!taxa_level !='unassigned') %>%
  # filter(!!taxa_level !='unknown') %>%
  # filter(!!taxa_level !='s_') %>%
  # filter(!!taxa_level !='g_') %>%
  unite(taxa_label, Class, Order, Family, Genus, sep='_') %>%
  group_by(taxa_label) %>%
  mutate(sum_per_tot = sum(per_tot)) %>%
  distinct(taxa_label,.keep_all = TRUE ) %>%
  arrange(-sum_per_tot) %>%
  select(taxa_label, sum_per_tot) %>%
  #print(n = Inf) %>%
  ungroup() %>%
  select(taxa_label, sum_per_tot) %>%
  top_n(20)

# assign text colour
library(ggthemes)
textcol <- "grey40"
print("Begin plotting...")
bp_top <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  inner_join(taxa_new %>% rename(ASV = `#OTUID`),  by = c("ASV")) %>%  #join with taxonomy
  #make taxa label
  unite(taxa_label, Class, Order, Family, Genus, sep='_') %>%
  right_join(top_taxa) %>% #limit to top taxa
  ggplot(aes(x = fct_reorder(SampleID, x), y = per_tot)) +
  geom_bar(stat = "identity", aes(fill = taxa_label))+
  scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="Percent Total Reads")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    axis.text.y=element_text(size=6,colour=textcol),
    axis.title.y = element_text(size=6),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())

filename = paste(plot_dir, marker,'_top20',taxa_level,'_bar_comp.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

#plot cluster groups?
bp_side <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  ggplot(aes(x = fct_reorder(SampleID, x), y = 1)) +
  geom_bar(stat = "identity", aes(fill = cluster_6))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="clust")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=2)) +
  coord_flip() +
  theme(
    #legend
    legend.position="bottom",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=8,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=8,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())

filename = paste(plot_dir, marker,'_cluster6_.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

# bp_side2 <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
#   ggplot(aes(x = fct_reorder(SampleID, x), y = 1)) +
#   geom_bar(stat = "identity", aes(fill = depth))+
#   #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
#   labs(x="",y="Total Reads")+
#   theme_minimal() +
#   guides(fill=guide_legend(ncol=1)) +
#   coord_flip() +
#   theme(
#     #legend
#     legend.position="right",legend.direction="vertical",
#     legend.text=element_text(colour=textcol,size=8,face="bold"),
#     legend.key.height=grid::unit(0.3,"cm"),
#     legend.key.width=grid::unit(0.3,"cm"),
#     legend.title=element_text(colour=textcol,size=8,face="bold"),
#     axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=5,colour=textcol),
#     #axis.text.x=element_text(size=7,colour=textcol),
#     #axis.text.y=element_text(size=6,colour=textcol),
#     #axis.title.y = element_text(size=6),
#     axis.line.y=element_blank(),
#     axis.ticks.y=element_blank(),
#     axis.text.y=element_blank(),
#     axis.title.y=element_blank(),
#     plot.background=element_blank(),
#     panel.border=element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.grid.major = element_line(size = .25),
#     plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
#     plot.title=element_blank())


bp_side2 <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  ggplot(aes(x = fct_reorder(SampleID, x), y = depth)) +
  #geom_bar(stat = "identity", aes(fill = depth))+
  geom_point(aes(shape=ESP,color = diel))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="depth(m)")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())


bp_side3 <- inner_join(potu_new2, tree_data,  by = c("SampleID")) %>% #join with metadata
  #mutate(local_time = mdy_hms(local_time)) %>%
  ggplot(aes(x = fct_reorder(SampleID, x), y = local_time)) +
  #geom_bar(stat = "identity", aes(fill = depth))+
  geom_point(aes(shape=ESP,color = diel))+
  #scale_fill_tableau(palette = "Tableau 20", type = c("regular"), direction = 1)+
  labs(x="",y="time")+
  theme_minimal() +
  guides(fill=guide_legend(ncol=1)) +
  coord_flip() +
  theme(
    #legend
    legend.position="right",legend.direction="vertical",
    legend.text=element_text(colour=textcol,size=3,face="bold"),
    legend.key.height=grid::unit(0.3,"cm"),
    legend.key.width=grid::unit(0.3,"cm"),
    legend.title=element_text(colour=textcol,size=3,face="bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1,size=3,colour=textcol),
    #axis.text.x=element_text(size=7,colour=textcol),
    #axis.text.y=element_text(size=6,colour=textcol),
    #axis.title.y = element_text(size=6),
    axis.line.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    plot.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = .25),
    plot.margin=margin(0.1,0.1,0.1,0.1,"cm"),
    plot.title=element_blank())



#cluster plot  
cluster_plot <- ggplot() + 
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1)+
  #geom_bar(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=depth),alpha=1, size=1) +
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend), size=0.2, color='darkgrey') +
  #geom_rect(data=tree_data, aes(xmin=x,xmax = x+.01, ymin=y-1,ymax=y-2, color=year_char),alpha=1, size=1)+
  #geom_text(data=tree_data, aes(x=x, y=y, label=diel, hjust=-.4), size=1) +
  #geom_text(data=tree_data, aes(x=x, y=y, label=PlateID, hjust=-6), size=2) +
  coord_flip() + scale_y_reverse() + 
  scale_color_viridis(option="viridis")+
  #scale_color_brewer(palette='Set1')+
  theme(axis.line=element_blank(),
        axis.ticks=element_blank(),
        axis.text=element_blank(),
        axis.title=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank())

# library(gridExtra)
# grid.arrange(cluster_plot, bp_top, ncol=2)
# 
# gA <- ggplotGrob(A)
# gB <- ggplotGrob(B)
# maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5])
# gA$widths[2:5] <- as.list(maxWidth)
# gB$widths[2:5] <- as.list(maxWidth)
# grid.arrange(gA, gB, ncol=1)
#   
# 
# gA <- ggplotGrob(bp_side)
# gB <- ggplotGrob(bp_top)
# grid::grid.newpage()
# grid::grid.draw(rbind(gA, gB))

library(cowplot)
#plot_grid(bp_side+guides(fill="none"), bp_top+guides(fill="none"), labels = c('A', 'B'), label_size = 12)

plot_grid(cluster_plot+guides(fill="none", color="none"),bp_side+guides(fill="none"),bp_side2+guides(fill="none"), bp_top, label_size = 6, align = "h", ncol=4, rel_widths=c(2,0.5,1,5))

filename = paste(plot_dir, marker,'_cluster_top20_depth.png', sep='')
#print('Plot of top 20 Genus average by month:')
print(filename)
ggsave(filename,height = 6, width =10, units = 'in')

```




